Datasheet for 'Diamond dataset

### 2024-12-03 others/datasheet/datasheet_template.qmd
upload datasheet qmd and pdf

---
title: "Datasheet for 'Diamond dataset'"
author: 
  - Yawen Tan
thanks: "Code and data are available at:  [https://github.com/YawennnnnnTan/Analysis-of-Diamond-Price]"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references .bib
---

Extract of the questions from @gebru2021datasheets.

The dataset discussed in this datasheet is 'Diamonds' [@diamonds_data].

>>>>

---
title: "Datasheet for 'Diamond dataset'"
author: 
  - Yawen Tan
thanks: "Code and data are available at:  [https://github.com/YawennnnnnTan/Analysis-of-Diamond-Price]"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.
The dataset discussed in this datasheet is 'Diamonds' [@diamonds_data].
